\section{Introduction}
\label{sec:Introduction}
%
In recent years, the increasing size of the dataset collected
by LHCb, has led to renewed interest in fast simulation. In this note the
mass resolution for the decay $\chi_{c1} \rightarrow J/\psi \mu^+ \mu^-$ is studied and
an emulator developed to reproduce the performance of the full
simulation. The studies were done with a
particular application in mind: accurately simulating the similar
decay  $\chi_{b} \rightarrow \Upsilon \mu^+ \mu^-$ in the \textbf{RapidSim}
framework~\cite{Cowan:2016tnm}. It is planned to use this mode to
measure the mass and width of the $\chi_b$
states. 

A puzzle from the study of the resonance parameters of the $\chi_c$ states in
Ref. \cite{Anderlini:2270922} was that \textbf{RapidSim} over-estimated the momentum
resolution by around $30 \%$ \cite{LHCb-PAPER-2017-036}. This is
despite that \textbf{RapidSim} has realistic models of both the
the momentum and track slope resolution taken from Ref. \cite{Needham:1080556} and
kinematic reweighting was performed. For use in the $\chi_{b}$
study this discrepancy needs to be understood and the resolution model
in \textbf{RapidSim} improved. The insights and knowledge gained in
achieving this goal have more general
applicability. 

This note is laid out as follows. First, the datasets and selections
used are defined. Following this a model for the  $\chi_{c1} \rightarrow J/\psi \mu^+ \mu^-$ mass resolution is
developed. Finally, the model is validated using this mode together
with the $\chi_{c2} \rightarrow J/\psi \mu^+ \mu^-$, 
$\psi(2S) \rightarrow J/\psi \pi^+ \pi^-$ and $X(3872) \rightarrow
J/\psi \pi^+ \pi^-$ decay modes. 